Cannibalism among the supermassive black holes

### 2018-09-17 paper.tex
Modified/added results plots

\section{Results}\label{sec:results}
\begin{figure}[H]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/Summary_Results_All_Galaxies.png}
\caption{Histogram of merged, ejected, and orbiting SMBHs}
\label{fig:meosmbh}
\end{center}
\end{figure}

>>>>

\section{Results}\label{sec:results}
\begin{figure}[h!]
\begin{center}
\includegraphics[width=0.45\textwidth]{"plots/Fractions All Galaxies".png}
\caption{Fractions Merged/Ejected/Orbiting at z=0, by mass bin}
\label{fig:fmeo}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.45\textwidth]{plots/"Final Luminosities of Oriting BHs".png}
\caption{Luminosities of Orbiting BHs at z=0}
\label{fig:loobhs}
\end{center}
\end{figure}
